---
title: "Random Forest"
author: "James Browne"
date: "November 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
'''{r, echo=FALSE }
install.packages('randomForest_4.6-13.tar.gz', repos=NULL)
library(randomForest)
set.seed(71)
mydata = read.table("R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
'''
## R Markdown

Test 1: 5 runs of Breiman RF on breast-cancer-wisc

```{r , echo=FALSE}
library(randomForest)
getwd()
mydata = read.table("~/R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
x <- vector()
for (i in 1:5){
  iris.rf<-randomForest(clase ~ ., data=mydata, importance=TRUE, proximity=TRUE, rerf=20)
x <- c(x,round(iris.rf$err.rate[iris.rf$ntree]*100, digits=2))
}
mean(x)
```

Test 2: 5 runs, A = dense matrix, mdim x mtry, breast-cancer-wisc

```{r , echo=FALSE}
library(randomForest)
getwd()
mydata = read.table("~/R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
x <- vector()
for (i in 1:5){
  iris.rf<-randomForest(clase ~ ., data=mydata, importance=TRUE, proximity=TRUE, rerf=3)
x <- c(x,round(iris.rf$err.rate[iris.rf$ntree]*100, digits=2))
}
mean(x)
```

Test 3: 5 runs, A = dense matrix, mdim x mdim, breast-cancer-wisc

```{r , echo=FALSE}
library(randomForest)
getwd()
mydata = read.table("~/R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
x <- vector()
for (i in 1:5){
  iris.rf<-randomForest(clase ~ ., data=mydata, importance=TRUE, proximity=TRUE, rerf=4)
x <- c(x,round(iris.rf$err.rate[iris.rf$ntree]*100, digits=2))
}
mean(x)
```


Test 4: 5 runs, A = sparse matrix, mdim x mtry, breast-cancer-wisc

```{r , echo=FALSE}
library(randomForest)
getwd()
mydata = read.table("~/R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
x <- vector()
for (i in 1:5){
  iris.rf<-randomForest(clase ~ ., data=mydata, importance=TRUE, proximity=TRUE, rerf=6)
x <- c(x,round(iris.rf$err.rate[iris.rf$ntree]*100, digits=2))
}
mean(x)
```

Test 5: 5 runs, A = sparse matrix, mdim x mdim, breast-cancer-wisc

```{r , echo=FALSE}
library(randomForest)
getwd()
mydata = read.table("~/R/data/breast-cancer-wisc/breast-cancer-wisc_R.dat")
mydata$clase <- as.factor(mydata$clase)
x <- vector()
for (i in 1:5){
  iris.rf<-randomForest(clase ~ ., data=mydata, importance=TRUE, proximity=TRUE, rerf=7)
x <- c(x,round(iris.rf$err.rate[iris.rf$ntree]*100, digits=2))
}
mean(x)
```