---
title: "RerF experiments on iris and breast-cancer-wisc"
author: "James Browne"
date: "November 15, 2016"
output: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE, message=FALSE, cache = TRUE)
library(randomForest)
```
For all experiments-
number of trees = 500
mtry = mdim^.5


**********************************************************************************
Experiment 1-  Run 100 rounds.  Each round: randomly select 80% of iris.  Run classifier.
**********************************************************************************

Classifier- RF
```{r C_RF_iris, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,])
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_3_iris, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=3)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_6_iris, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=6)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_4_iris, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=4)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_7_iris, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=7)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```


**********************************************************************************
Experiment 2-  Run 100 rounds.  Each round: Train using Trunk_XTrain.  Run classifier.
**********************************************************************************

Classifier- RF
```{r C_RF_trunk, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
trunkX<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Xtrain.dat", header=FALSE)
trunkY<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Ytrain.dat", header=FALSE)
trunkY<- factor(data.matrix(trunkY))
library(randomForest)
results = vector()

for (i in 1:100){
trunk.rf <- randomForest(trunkX, trunkY)
results[i] <- trunk.rf$err.rate[trunk.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_3_trunk, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
trunkX<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Xtrain.dat", header=FALSE)
trunkY<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Ytrain.dat", header=FALSE)
trunkY<- factor(data.matrix(trunkY))
library(randomForest)
results = vector()

for (i in 1:100){
trunk.rf <- randomForest(trunkX, trunkY, RerF=3)
results[i] <- trunk.rf$err.rate[trunk.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_6_trunk, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
trunkX<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Xtrain.dat", header=FALSE)
trunkY<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Ytrain.dat", header=FALSE)
trunkY<- factor(data.matrix(trunkY))
library(randomForest)
results = vector()

for (i in 1:100){
trunk.rf <- randomForest(trunkX, trunkY, RerF=6)
results[i] <- trunk.rf$err.rate[trunk.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_4_trunk, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
trunkX<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Xtrain.dat", header=FALSE)
trunkY<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Ytrain.dat", header=FALSE)
trunkY<- factor(data.matrix(trunkY))
library(randomForest)
results = vector()

for (i in 1:100){
trunk.rf <- randomForest(trunkX, trunkY, RerF=4)
results[i] <- trunk.rf$err.rate[trunk.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_7_trunk, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
trunkX<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Xtrain.dat", header=FALSE)
trunkY<- read.csv("~/gitRepos/old.RandomForest/Trunk/Trunk_Ytrain.dat", header=FALSE)
trunkY<- factor(data.matrix(trunkY))
library(randomForest)
results = vector()

for (i in 1:100){
trunk.rf <- randomForest(trunkX, trunkY, RerF=7)
results[i] <- trunk.rf$err.rate[trunk.rf$ntree]*100
}
summary(results)
```


**********************************************************************************
Experiment 3-  Run 100 rounds.  Each round: Train using Parity_Xtrain.  Run classifier.
**********************************************************************************

Classifier- RF
```{r C_RF_parity, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
ParityX<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Xtrain.dat", header=FALSE)
ParityY<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Ytrain.dat", header=FALSE)
ParityY<- factor(data.matrix(ParityY))
library(randomForest)
results = vector()

for (i in 1:100){
parity.rf <- randomForest(ParityX, ParityY)
results[i] <- parity.rf$err.rate[parity.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_3_parity, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
ParityX<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Xtrain.dat", header=FALSE)
ParityY<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Ytrain.dat", header=FALSE)
ParityY<- factor(data.matrix(ParityY))
library(randomForest)
results = vector()

for (i in 1:100){
parity.rf <- randomForest(ParityX, ParityY, RerF=3)
results[i] <- parity.rf$err.rate[parity.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_6_parity, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
ParityX<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Xtrain.dat", header=FALSE)
ParityY<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Ytrain.dat", header=FALSE)
ParityY<- factor(data.matrix(ParityY))
library(randomForest)
results = vector()

for (i in 1:100){
parity.rf <- randomForest(ParityX, ParityY, RerF=6)
results[i] <- parity.rf$err.rate[parity.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_4_parity, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
ParityX<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Xtrain.dat", header=FALSE)
ParityY<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Ytrain.dat", header=FALSE)
ParityY<- factor(data.matrix(ParityY))
library(randomForest)
results = vector()

for (i in 1:100){
parity.rf <- randomForest(ParityX, ParityY, RerF=4)
results[i] <- parity.rf$err.rate[parity.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r C_RerF_7_parity, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
ParityX<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Xtrain.dat", header=FALSE)
ParityY<- read.csv("~/gitRepos/old.RandomForest/Parity/Parity_Ytrain.dat", header=FALSE)
ParityY<- factor(data.matrix(ParityY))
library(randomForest)
results = vector()

for (i in 1:100){
parity.rf <- randomForest(ParityX, ParityY, RerF=7)
results[i] <- parity.rf$err.rate[parity.rf$ntree]*100
}
summary(results)
```