---
title: "RerF experiments on iris and breast-cancer-wisc"
author: "James Browne"
date: "November 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
For all experiments-




Experiment 1-  Run 100 rounds.  Each round: randomly select 80% of iris.  Run classifier.

Classifier- RF
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
library(randomForest)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,])
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
library(randomForest)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=3)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mdim
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
library(randomForest)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=6)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Dense A: mdim * (mdim -1) non zero entries all of which have 50/50 chance of being 1/-1.
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
library(randomForest)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=4)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```

Classifier- RerF
1.  A is mdim by mtry
2.  Sparse A: mdim non zero entries all of which have 50/50 chance of being 1/-1.
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
set.seed(71)
data(iris)
library(randomForest)
results = vector()

for (i in 1:100){
ind <- sample(2, nrow(iris), replace = TRUE, prob=c(0.8, 0.2))
iris.rf <- randomForest(Species ~ ., data=iris[ind ==1,], RerF=7)
results[i] <- iris.rf$err.rate[iris.rf$ntree]*100
}
summary(results)
```